%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents

This thesis is the result of the hard work of many people. Firstly, I would like to thank Rika Antonova, who has been a close collaborator and a very good friend through most of this work. The day I sat opposite to you at Commonplace Coffee and started chatting was a very lucky day. I could not have imagined that this day would shape the course of my PhD, and things I do beyond it. I hope we continue working closely in the future and keep coming up with cool ways of collaborating. 

Next, of course, comes my advisor, Chris Atkeson. I have always found Chris to be more of a friend than advisor, and I will miss our philosophical, political and academic discussions on Fridays. It seems strange to feel nostalgic about these, given how I dreaded them in my first year. But the meetings and Chris grow on you, eventually. Thank you, Chris, for giving me the freedom to do what I wanted, never pushing me to publish when I was not ready, and letting me focus completely on my research. Your big picture advice always helped me understand my research and how it relates to the rest of the world better. They say that you turn into your advisor by the end of your PhD, and I have no problems with that. Thanks for being awesome!

Then comes everyone at CMU who helped me get through these, often difficult, 4 years. I would have probably quit midway, if it wasn't for William Martin, Micheal Koval and Nitish Thatte. Thanks for helping me see the light at the end of the tunnel -- or rather, the next tunnel. I would also like to thank Yigit, Perry, Tianyu for their help with the different parts of my thesis. Thanks Jennifer, Venkat, Arun, Wen, Leo, Sam for the illuminating discussions, opinions and encouragements. 

I would also like to thank Hartmut Geyer for all his help through the last four years. Thanks for letting me into your lab meetings, and for your advice and discussions. Even though we sometimes disagreed, I always found great value in hearing your perspective on problems. Thanks to Stefan Schaal for always being there when I needed help and outsider's perspective. Stefan's selfless nature and advising style is something I will always strive for. Thanks Oliver for your help, opinions and advice during this work. 

Last but definitely not the least, I would like to thank my parents for being a constant source of support and entertainment. Thank you for your love, patience and for not badgering me to get married sooner.

\end{acknowledgements}